\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fancyhdr}

% Colors
\definecolor{sectioncolor}{RGB}{0,102,204}

% Header settings (only on first page)
\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{%
  \textbf{\Large YOGESH JOSHI}\\[2mm]
  \small Bangalore, KA 560102 \quad | \quad(IN) +91 8000038220 \quad | \quad
  \href{mailto:iyogeshjoshi@gmail.com}{iyogeshjoshi@gmail.com} \quad | \quad
  GitHub: \href{https://github.com/iyogeshjoshi}{iyogeshjoshi}
}
\fancypagestyle{plain}{\fancyhf{} \renewcommand{\headrulewidth}{0pt}}

% Section formatting
\titleformat{\section}{\color{sectioncolor}\Large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}
\titlespacing*{\section}{0pt}{12pt}{6pt}

\begin{document}
\thispagestyle{fancy}

%-----------------------------------------------
\section*{Professional Summary}
Results-driven Lead Software Engineer with \textbf{~12 years} of expertise in JavaScript and Full-stack development. Skilled in designing, developing, and optimizing scalable, high-performance software solutions. Experienced in architecting complex systems and leading teams to deliver innovative, user-centric applications. Passionate about driving technical excellence, fostering collaboration, and continuously learning to stay ahead in a dynamic industry.

%-----------------------------------------------
\section*{Skills}

\textbf{Technical Skills}
\begin{itemize}[leftmargin=*]
  \item \textbf{Languages \& Frameworks}: JavaScript (ES6+), TypeScript, Node.js, React.js, Redux, Angular, Vue.js, Next.js, Express.js, NestJS, Micro-Frontend React
  \item \textbf{Backend \& API Development}: RESTful APIs, GraphQL, WebSockets (Socket.io), Microservices Architecture, Serverless Computing (AWS Lambda, Firebase Functions)
  \item \textbf{Databases \& Storage}: PostgreSQL, MySQL, MongoDB, Redis, Firebase Firestore, IndexedDB
  \item \textbf{Data Visualization}: D3.js, Highcharts, Chart.js
  \item \textbf{Cloud \& DevOps}: AWS (EC2, S3, Lambda, DynamoDB, Aurora), Google Cloud, Firebase Toolchain, Docker, Kubernetes, CI/CD Pipelines, Mulesoft, Terraform
  \item \textbf{Performance \& Optimization}: Caching Strategies, Load Balancing, Code Profiling, Database Indexing, Frontend Optimization (Lazy Loading, Code Splitting)
  \item \textbf{Testing \& Quality Assurance}: Jest, Mocha, Chai, Cypress, Selenium, TDD/BDD
  \item \textbf{Security \& Authentication}: OAuth, JWT, SAML, Web Security Best Practices, OWASP Guidelines
  \item \textbf{Web \& Mobile Development}: PWA, React Native, Native iOS/Android SDKs, Google Maps SDK/APIs
\end{itemize}

\textbf{Soft Skills \& Leadership}
\begin{itemize}[leftmargin=*]
  \item \textbf{System Architecture \& Design Patterns}: MVC, MVVM, SOLID Principles, Event-Driven Architecture
  \item \textbf{Agile \& Team Leadership}: Scrum, Kanban, Sprint Planning, Mentorship \& Code Reviews
  \item \textbf{Problem-Solving \& Critical Thinking}: Debugging, Performance Tuning, Scalable System Design
  \item \textbf{Collaboration \& Communication}: Cross-functional Teamwork, Technical Documentation, Stakeholder Management
  \item \textbf{Time \& Project Management}: Prioritization, Estimation, Delivering within Deadlines
\end{itemize}

%-----------------------------------------------
\section*{Experience}

\subsection*{Lead Software Engineer | YARA International | Bengaluru, KA (Aug 2022 -- Feb 2025)}
\begin{itemize}[leftmargin=*]
  \item Brainstorming session with Product and Designers to simplify and define tasks for Devs.
  \item Developing complex architectural designs, implementing \& scaling them.
  \item Helping team understand complex concepts as well helping them grow with understanding of Software designs and patterns by hosting multiple learning sessions with team.
  \item Have updated the existing architecture on AWS to successfully reduce the cost significantly.
  \item Collaboration across team and function for successfully designing, developing \& maintaining the product.
  \item Implemented and maintained multiple Front-end applications as well as developed and deployed multiple micro service APIs required for them.
  \item Collaboration with UI/UX Designers \& Product for the user experience and journey across the product.
  \item Deployment of multiple services on Mulesoft Anypoint middleware and AWS.
\end{itemize}

\subsection*{Senior Software Engineer | YARA International | Bengaluru, KA (Aug 2020 -- Aug 2022)}
\begin{itemize}[leftmargin=*]
  \item Designed and Developed Mobile application using ReactNative, MobX, MobX State Tree, redux and other hybrid technologies.
  \item Managed new Interns and Trainees, and helped them on-board and learn new technologies and concepts.
  \item Helped Junior developers and colleagues with their tasks and fix issues when they are stuck.
  \item Managed release of application from internal releases to the play store releases.
  \item Created a micro-service architecture template using NestJs and other required plugins with Back-end team.
  \item Designed and developed Backend REST APIs for multiple modules.
  \item Developed and managed micro-services on Back-end using NestJs.
  \item Have added automations, small scripts, and other tools in place to automate daily mundane tasks and to maintain code hygiene and structure.
  \item Collaborated closely with other teams and Product Owners to complete features and finish the release cycle in all sprints.
\end{itemize}

\subsection*{Senior Software Engineer (Associate Manager) | Ather Energy Private Ltd. | Bengaluru, KA (Jun 2015 -- Aug 2020)}
\begin{itemize}[leftmargin=*]
  \item Designed and Developed Software application using ReactJs, Redux and other web technologies for the vehicle which is tightly integrated with other system-level applications.
  \item Designed and Developed Mobile Application using React Native to sync data across platforms from bike to cloud to the mobile app using Firebase toolchain.
  \item Designed and Developed Complete navigation using Vanilla Js/ ReactJS, and Google map js APIs, from scratch on the web platform to be able to use it on our Bike's hardware with limited hardware and memory restrictions.
  \item Identified performance issues in the application and implemented more optimized components.
  \item Mentored new joiners and trainees.
  \item Worked closely with the system team and helped them develop using Go-lang and integrate their app with UI App.
  \item Developed Coding, Documenting and other version control systems like Git and Gitlab standards and hygiene.
  \item Determine system performance standards.
  \item Automated several everyday mundane tasks for peers and QA to speed up the process using shell scripting or microservices.
  \item Developed several Software and services within and for other teams to help them analyze, track and solve problems using JavaScript web stack.
\end{itemize}

\subsection*{Software Artisan | Function Space | Bangalore, KA (May 2014 -- Jun 2015)}
\begin{itemize}[leftmargin=*]
  \item Developed Web applications and tested them for issues.
  \item Developed, Tested and Maintain online Science forum community platform using PHP, JavaScript, and other web stacks technologies.
  \item Created several applications to help users learn and play at the same time.
  \item Learnise - complete learning ecosystem for all the students and teachers, by providing them tools like online IDEs to learn and run on the go.
  \item Play Physics - it is the new way to learn by playing interactive games and interactive quizzes based on science and physics concepts.
  \item Developed several internal multi-tier dashboards and tools to analyze, track and monitor user's data, behavior, and actions.
  \item Worked closely with sale and product team to understand user's requirements and with Design and testing team to develop it and test it thoroughly.
\end{itemize}

\subsection*{Fullstack Software Developer | Avinashi Ventures Pvt Ltd | Surat, GJ (Jun 2013 -- Apr 2014)}
\begin{itemize}[leftmargin=*]
  \item BizBrain - Developed a complete HRMS system using AngularJs, NodeJs, Highcharts, and MongoDB.
  \item Developed and maintained a bulk telemarketing SMS delivery system using NodeJs and AT commands and integrated the same with other applications like BizBrain for delivering and taking system related alerts and inputs respectively.
  \item Developed mail delivery system to fetch, update and generate reports with charts and deliver it to the respective person automatically using NodeJs, PHP and MongoDB.
\end{itemize}

%-----------------------------------------------
\section*{Education}
\textbf{Bachelor of Engineering: Computer Engineering (2009 - 2013)} \\
Gujarat Technological University (GTU), Surat, GJ \\
CGPA: 8.05

%-----------------------------------------------
\section*{Additional Information}
\begin{itemize}[leftmargin=*]
  \item Hobbies include game development and home automation.
  \item Regular contributor to open-source software projects.
  \item Playing various genres of games.
\end{itemize}

\end{document}
